Resurgence of the Airy function

### 2022-07-08 airy-resurgence.tex
Try solving in weighted L^infinity spaces

\begin{align*}
\|\mathcal{G}f\|_p^p & = \int_{a \in \partial D} \left|\int_{\zeta(a') = 0}^{a} g(a, a')\,f(a')\,d\zeta(a') \right|^p\,\frac{|d\zeta(a)|}{2\pi R} \\
& \le \int_{a \in \partial D} \left(\int_{\zeta(a') = 0}^{a} |g(a, a')\,f(a')|\,|d\zeta(a')| \right)^p\,\frac{|d\zeta(a)|}{2\pi R} \\
\end{align*}
Since $\zeta = 0$ and $a$ are both in $\partial D$, and we're assuming that $f$ extends continuously to $\partial D$, we can compute $[\mathcal{G}f](a)$ using an integration path that runs along $\partial D$.
\begin{align*}
\|\mathcal{G}f\|_p^p & \le \int_{a \in \partial D} \left(\int_{a' \in \partial D} |g(a, a')\,f(a')|\,|d\zeta(a')| \right)^p\,\frac{|d\zeta(a)|}{2\pi R} \\
& = \int_{a \in \partial D} \left(2\pi R \int_{a' \in \partial D} |g(a, a')\,f(a')|\,\frac{|d\zeta(a')|}{2\pi R} \right)^p\,\frac{|d\zeta(a)|}{2\pi R} \\
& = (2\pi R)^p \int_{a \in \partial D} \|g(a, \cdot)\,f\|_1^p\;\frac{|d\zeta(a)|}{2\pi R}.
\end{align*}
Then, by H\"{o}lder's inequality,
\begin{align*}
\|\mathcal{G}f\|_p^p & \le (2\pi R)^p \int_{a \in \partial D} \|g(a, \cdot)\|_q^p\;\|f\|_p^p\;\frac{|d\zeta(a)|}{2\pi R} \\
& \le \|f\|_p^p\;(2\pi R)^p \int_{a \in \partial D} \|g(a, \cdot)\|_q^p\;\frac{|d\zeta(a)|}{2\pi R} \\
& \le \|f\|_p^p\;(2\pi R)^p \int_{a \in \partial D} \left( \int_{a' \in \partial D} |g(a, a')|^q\,\frac{|d\zeta(a')|}{2\pi R} \right)^{p/q}\,\frac{|d\zeta(a)|}{2\pi R}.
\end{align*}
Since we're assuming $p \le q$, we can apply Jensen's inequality to the concave function $(\cdot)^{p/q}$ and conclude that
\begin{align*}
\|\mathcal{G}f\|_p^p & \le \|f\|_p^p\;(2\pi R)^p \left( \int_{a \in \partial D} \int_{a' \in \partial D} |g(a, a')|^q\,\frac{|d\zeta(a')|}{2\pi R}\,\frac{|d\zeta(a)|}{2\pi R} \right)^{p/q} \\
& = \|f\|_p^p\;(2\pi R)^p\,\|g\|_q^p,
\end{align*}
which simplifies to
\[ \|\mathcal{G}f\|_p \le \|f\|_p\;2\pi R\,\|g\|_q. \]
That means
\[ \|\mathcal{G}\| \le 2\pi R\,\|g\|_q, \]
where the norm of $g$ is taken with respect to the rotation-invariant probability measure on $(\partial D)^2$.

\color{DodgerBlue}
\subsubsection{Algebraic integral operators}
Take a simply connected open set $\Omega \subset \C$ that touches but doesn't contain $\zeta = 0$. Let $\holoL{\infty}(\Omega)$ be the space of bounded holomorphic functions on $\Omega$ with the supremum norm $\|\cdot\|_\infty$. Let $\mathcal{S} \subset \holoL{\infty}(\Omega)$ be the union of $O_{\zeta, 0 \leftarrow}(\zeta^\tau)$ over all $\tau > 0$.

We'll study integral operators $\mathcal{G} \acts \holoL{\infty}(\Omega)$ of the form
\[ [\mathcal{G}f](a) = \int_{\zeta = 0}^{a} g(a, \cdot)\,f\,d\zeta, \]
where the kernel $g$ is an algebraic function over $\C^2$ which can be singular on $\Delta$, the diagonal.\footnote{Thanks to Alex Takeda for suggesting this.} To avoid ambiguity, we fix a branch of $g$ to use at the start of the integration path. The domain of $g$ is a covering of $\C^2$ which can be branched over $\Delta$. Continuing $g$ around $\Delta$ changes its phase by a root of unity, leaving its absolute value the same \textbf{[check]}. That makes $|g|$ a well-defined function on $\C^2 \smallsetminus \Delta$, which we can use to bound $\|\mathcal{G}\|$.

For each $a \in \C$, the expression $|g(a, \cdot)\,d\zeta|$ defines a {\em density} on $\Omega \smallsetminus \{a\}$---a norm on the tangent bundle which is compatible with the conformal structure. The square of a density is a Riemannian metric. Let $\ell_{g, \Omega}(a)$ be the distance from $\zeta = 0$ to $a$ with respect to the density $|g(a, \cdot)\,d\zeta|$ on $\Omega \smallsetminus \{a\}$. The bound
\begin{align*}
\big|[\mathcal{G}f](a)\big| & \le \left| \int_{\zeta = 0}^{a} g(a, \cdot)\,f\,d\zeta \right| \\
& \le \int_{\zeta = 0}^{a} |f|\,|g(a, \cdot)\,d\zeta| \\
& \le \|f\|_\infty \int_{\zeta = 0}^{a} |g(a, \cdot)\,d\zeta|
\end{align*}
holds for any integration path. Taking the infimum over all paths, we see that
\[ \big|[\mathcal{G}f](a)\big| \le \ell_{g, \Omega}(a)\,\|f\|_\infty. \]
so $\|\mathcal{G}\| \le \sup_{a \in \Omega} \ell_{g, \Omega}(a)$. Crucially, we can always make $\|\mathcal{G}\|$ a contraction by restricting $\Omega$.
\subsubsection{The example of fractional integrals}
Setting $g(a, a') = (\zeta(a) - \zeta(a'))^{-\lambda-1}$ with $\lambda \in (-\infty, 0)$, we get the fractional integral $\partial^\lambda_{\zeta \text{ from } 0}$. The density $|\zeta(a) - \zeta|^{-\lambda-1}\,|d\zeta|$ is rotationally symmetric around $a$, so the shortest path from $\zeta = 0$ to $a$ is a straight line with respect to $|d\zeta|$ \textcolor{magenta}{[check]}. It follows that
\begin{align*}
\ell_{g, \Omega}(a) & = \int_0^{|\zeta(a)|} t^{-\lambda-1}\,dt \\
& = -\tfrac{1}{\lambda} |\zeta(a)|^{-\lambda},
\end{align*}
so
\[ \|\partial^\lambda_{\zeta \text{ from } 0}\| \le \sup_\Omega {(-\tfrac{1}{\lambda}) |\zeta|^{-\lambda}}. \]
In particular, when $\Omega$ is small enough that $\|\zeta\|_\infty < 1$, the operator $\partial^\lambda_{\zeta \text{ from } 0}$ is a contraction of $\holoL{\infty}(\Omega)$ for all $\lambda \in (-\infty, -1]$.
\subsubsection{Fractional integral equations near a regular singular point}
Consider an integral operator $\mathcal{J}$ of the form
\[ p + \partial^{-1}_{\zeta \text{ from } 0} \circ q + \sum_{\lambda \in \Lambda} \partial^\lambda_{\zeta \text{ from } 0} \circ r_\lambda, \]
where:
\begin{itemize}
\item $\Lambda$ is a countable subset of $(-\infty, -1)$.
\item $p$, $q$, and $r_\lambda$ are functions in $\holoL{\infty}(\Omega)$ that extend holomorphically over $\zeta = 0$.
\item $p$ has a first-order zero at $\zeta = 0$.
\end{itemize}

>>>>

\color{DarkBlue}
\begin{align*}
\|\mathcal{G}f\|_1 & = \int_{a \in \partial D} \left| \int_{\zeta = 0}^{a} g(a, \cdot)\,f\,d\zeta \right|\,\frac{|d\zeta(a)|}{2\pi R} \\
& \le \int_{a \in \partial D} \left( \int_{\zeta = 0}^{a} |f|\,|g(a, \cdot)\,d\zeta| \right)\,\frac{|d\zeta(a)|}{2\pi R} \\
& \le \left( \sup_D |f| \right) \int_{a \in \partial D} \left( \int_{\zeta = 0}^{a} |g(a, \cdot)\,d\zeta| \right)\,\frac{|d\zeta(a)|}{2\pi R}.
\end{align*}
By the maximum principle, $\sup_D |f| = \sup_{\partial D} |f|$, so
\[ \|\mathcal{G}f\|_1 \le \|f\|_\infty \int_{a \in \partial D} \left( \int_{\zeta = 0}^{a} |g(a, \cdot)\,d\zeta| \right)\,\frac{|d\zeta(a)|}{2\pi R}. \]
Taking the infimum over all the integration paths we could use to evaluate $[\mathcal{G}f](a)$, we see that
\[ \|\mathcal{G}f\|_1 \le \|f\|_\infty \int_{a \in \partial D} \ell_{g, D}(a)\,\frac{|d\zeta(a)|}{2\pi R}. \]
\color{black}

\begin{align*}
\|\mathcal{G}f\|_p^p & = \int_{a \in \partial D} \left| \int_{\zeta(a') = 0}^{a} g(a, a')\,f(a')\,d\zeta(a') \right|^p\,\frac{|d\zeta(a)|}{2\pi R} \\
& \le \int_{a \in \partial D} \left( \int_{\zeta(a') = 0}^{a} |g(a, a')\,f(a')|\,|d\zeta(a')| \right)^p\,\frac{|d\zeta(a)|}{2\pi R} \\
\end{align*}
Since $\zeta = 0$ and $a$ are both in $\partial D$, and we're assuming that $f$ extends continuously to $\partial D$, we can compute $[\mathcal{G}f](a)$ using an integration path that runs along $\partial D$.
\begin{align*}
\|\mathcal{G}f\|_p^p & \le \int_{a \in \partial D} \left(\int_{a' \in \partial D} |g(a, a')\,f(a')|\,|d\zeta(a')| \right)^p\,\frac{|d\zeta(a)|}{2\pi R} \\
& = \int_{a \in \partial D} \left(2\pi R \int_{a' \in \partial D} |g(a, a')\,f(a')|\,\frac{|d\zeta(a')|}{2\pi R} \right)^p\,\frac{|d\zeta(a)|}{2\pi R} \\
& = (2\pi R)^p \int_{a \in \partial D} \|g(a, \cdot)\,f\|_1^p\;\frac{|d\zeta(a)|}{2\pi R}.
\end{align*}
Then, by H\"{o}lder's inequality,
\begin{align*}
\|\mathcal{G}f\|_p^p & \le (2\pi R)^p \int_{a \in \partial D} \|g(a, \cdot)\|_q^p\;\|f\|_p^p\;\frac{|d\zeta(a)|}{2\pi R} \\
& \le \|f\|_p^p\;(2\pi R)^p \int_{a \in \partial D} \|g(a, \cdot)\|_q^p\;\frac{|d\zeta(a)|}{2\pi R} \\
& \le \|f\|_p^p\;(2\pi R)^p \int_{a \in \partial D} \left( \int_{a' \in \partial D} |g(a, a')|^q\,\frac{|d\zeta(a')|}{2\pi R} \right)^{p/q}\,\frac{|d\zeta(a)|}{2\pi R}.
\end{align*}
Since we're assuming $p \le q$, we can apply Jensen's inequality to the concave function $(\cdot)^{p/q}$ and conclude that
\begin{align*}
\|\mathcal{G}f\|_p^p & \le \|f\|_p^p\;(2\pi R)^p \left( \int_{a \in \partial D} \int_{a' \in \partial D} |g(a, a')|^q\,\frac{|d\zeta(a')|}{2\pi R}\,\frac{|d\zeta(a)|}{2\pi R} \right)^{p/q} \\
& = \|f\|_p^p\;(2\pi R)^p\,\|g\|_q^p,
\end{align*}
which simplifies to
\[ \|\mathcal{G}f\|_p \le \|f\|_p\;2\pi R\,\|g\|_q. \]
That means
\[ \|\mathcal{G}\| \le 2\pi R\,\|g\|_q, \]
where the norm of $g$ is taken with respect to the rotation-invariant probability measure on $(\partial D)^2$.

\color{DarkBlue}
\subsubsection{Algebraic integral operators}
Take a simply connected open set $\Omega \subset \C$ that touches but doesn't contain $\zeta = 0$. Let $\holoL{\infty}(\Omega)$ be the space of bounded holomorphic functions on $\Omega$ with the supremum norm $\|\cdot\|_\infty$. Multiplying by $\zeta^{-\sigma}$ maps $\holoL{\infty}(\Omega)$ isomorphically onto another space of holomorphic functions on $\Omega$. We'll call this space $\holoL{\infty, \sigma}(\Omega)$ and give it the norm $\|f\|_{\infty, \sigma} = \|\zeta^\sigma f\|_\infty$, so that
\begin{align*}
\holoL{\infty}(\Omega) & \to \holoL{\infty, \sigma}(\Omega) \\
\phi & \mapsto \zeta^{-\sigma} \phi
\end{align*}
is an isometry.

%%Let $\mathcal{S} \subset \holoL{\infty}(\Omega)$ be the union of $O_{\zeta, 0 \leftarrow}(\zeta^\tau)$ over all $\tau > 0$.

We'll study integral operators $\mathcal{G} \acts \holoL{\infty, \sigma}(\Omega)$ of the form
\[ [\mathcal{G}f](a) = \int_{\zeta = 0}^{a} g(a, \cdot)\,f\,d\zeta, \]
where the kernel $g$ is an algebraic function over $\C^2$ which can be singular on $\Delta$, the diagonal.\footnote{Thanks to Alex Takeda for suggesting this.} To avoid ambiguity, we fix a branch of $g$ to use at the start of the integration path. The domain of $g$ is a covering of $\C^2$ which can be branched over $\Delta$. Continuing $g$ around $\Delta$ changes its phase by a root of unity, leaving its absolute value the same \textbf{[check]}. That makes $|g|$ a well-defined function on $\C^2 \smallsetminus \Delta$, which we can use to bound $\|\mathcal{G}\|$.

For each $a \in \C$, the expression $|g(a, \cdot)\,d\zeta|$ defines a {\em density} on $\Omega \smallsetminus \{a\}$---a norm on the tangent bundle which is compatible with the conformal structure. The square of a density is a Riemannian metric. Let $\ell_{g, \sigma, \Omega}(a)$ be the distance from $\zeta = 0$ to $a$ with respect to the density $|\zeta(a)^\sigma\,g(a, \cdot)\,\zeta^{-\sigma} d\zeta|$ on $\Omega \smallsetminus \{a\}$. The bound
\begin{align*}
\big|[\zeta^\sigma \mathcal{G}f](a)\big| & \le \left| \zeta(a)^\sigma \int_{\zeta = 0}^{a} g(a, \cdot)\,f\,d\zeta \right| \\
& \le \int_{\zeta = 0}^{a} |\zeta^\sigma f|\,|\zeta(a)^\sigma\,g(a, \cdot)\,\zeta^{-\sigma}\,d\zeta| \\
& \le \|f\|_{\infty, \sigma} \int_{\zeta = 0}^{a} |\zeta(a)^\sigma\,g(a, \cdot)\,\zeta^{-\sigma}\,d\zeta|
\end{align*}
holds for any integration path. Taking the infimum over all paths, we see that
\[ \big|[\mathcal{G}f](a)\big| \le \ell_{g, \sigma, \Omega}(a)\,\|f\|_\infty. \]
so $\|\mathcal{G}\| \le \sup_{a \in \Omega} \ell_{g, \sigma, \Omega}(a)$. Crucially, we can always make $\|\mathcal{G}\|$ a contraction by restricting $\Omega$.
\subsubsection{The example of fractional integrals}
Setting
\[ g(a, a') = \zeta(a)^\rho\,(\zeta(a) - \zeta(a'))^{-\lambda-1}\,\zeta(a')^\mu \]
with $\lambda \in (-\infty, 0)$, we get the operator
\[ \zeta^\rho \circ \partial^\lambda_{\zeta \text{ from } 0} \circ \zeta^\mu. \]
The shortest path from $\zeta = 0$ to $a$ with respect to $|\zeta(a)^\sigma\,g(a, \cdot)\,\zeta^{-\sigma}\,d\zeta|$ is the same as the shortest path with respect to $|d\zeta|$ \textcolor{magenta}{[check]}. It follows that
\begin{align*}
\ell_{g, \sigma, \Omega}(a) & = \int_0^{|\zeta(a)|} |\zeta(a)|^{\rho+\sigma}\,(|\zeta(a)| - r)^{-\lambda-1}\,r^{\mu-\sigma}\,dr \\
& = |\zeta(a)|^{\rho+\sigma} \int_0^1 \,(|\zeta(a)| - |\zeta(a)| t)^{-\lambda-1}\,(|\zeta(a)| t)^{\mu-\sigma}\,|\zeta(a)|\,dt \\
& = |\zeta(a)|^{\rho+\sigma-\lambda-1+\mu-\sigma+1} \int_0^1 \,(1-t)^{-\lambda-1}\,t^{\mu-\sigma}\,dt \\
& = |\zeta(a)|^{\rho-\lambda} \int_0^1 \,(1-t)^{-\lambda-1}\,t^{\mu-\sigma}\,dt \\
& = |\zeta(a)|^{\rho-\lambda+\mu}\,B(-\lambda, \mu-\sigma+1),
\end{align*}
where $B$ is the beta function. Hence, on $\holoL{\infty, \sigma}(\Omega)$,
\[ \|\zeta^\rho \circ \partial^\lambda_{\zeta \text{ from } 0} \circ \zeta^\mu\| \le B(-\lambda,\mu-\sigma+1)\,\sup_\Omega |\zeta|^{\rho-\lambda+\mu}. \]
In particular, when $\Omega$ is small enough that \textcolor{magenta}{[???]}, the operator on the left-hand side is a contraction of $\holoL{\infty, \sigma}(\Omega)$ for all $\lambda \in (-\infty, -\rho]$.
\subsubsection{Fractional integral equations near a regular singular point}
Consider an integral operator $\mathcal{J}$ of the form
\[ p + \partial^{-1}_{\zeta \text{ from } 0} \circ q + \sum_{\lambda \in \Lambda} \partial^\lambda_{\zeta \text{ from } 0} \circ r_\lambda, \]
where:
\begin{itemize}
\item $\Lambda$ is a countable subset of $(-\infty, -1)$.
\item $p$, $q$, and $r_\lambda$ are functions in $\holoL{\infty}(\Omega)$ that extend holomorphically over $\zeta = 0$.
\item $p$ has a first-order zero at $\zeta = 0$.
\end{itemize}

\textcolor{Indigo}{We want to solve the equation $\mathcal{J}f = 0$. Let's look for a solution of the form $f = \zeta^{\tau-1}(1 + \tilde{f})$ with $\tau \in (0, \infty)$ and $\tilde{f} \in \holoL{\infty}(\Omega)$.}

Let $p'_0$ and $q_0$ be the values of $\tfrac{\partial}{\partial \zeta} p$ and $q$, respectively, at $\zeta = 0$. Since $p$, $q$, and $r_\lambda$ extend holomorphically over $\zeta = 0$, and $p$ vanishes at $\zeta = 0$, we can write
\begin{alignat*}{2}
p & = p'_0 \zeta &\;+\;& \tilde{p} \zeta^2 \\
q & = q_0 &\;+\;& \tilde{q} \zeta
\end{alignat*}
where $\tilde{p}, \tilde{q} \in \holoL{\infty}(\Omega)$ extend holomorphically over $\zeta = 0$ too. Then we have
\begin{align*}
\mathcal{J} & = (p_0'\zeta + \tilde{p}\zeta^2) + (q_0\,\partial^{-1}_{\zeta \text{ from } 0} + \partial^{-1}_{\zeta \text{ from } 0} \circ \zeta \circ \tilde{q}) + \sum_{\lambda \in \Lambda} \partial^\lambda_{\zeta \text{ from } 0} \circ r_\lambda \\
& = p'_0\zeta + q_0\,\partial^{-1}_{\zeta \text{ from } 0} + \zeta \circ \tilde{\mathcal{J}},
\end{align*}
where
\[ \tilde{\mathcal{J}} = \tilde{p}\zeta + (\zeta^{-1} \circ \partial^{-1}_{\zeta \text{ from } 0} \circ \zeta) \circ \tilde{q} + \sum_{\lambda \in \Lambda} (\zeta^{-1} \circ \partial^\lambda_{\zeta \text{ from } 0}) \circ r_\lambda. \]
For any $\tau \in (0, \infty)$,
\[ \mathcal{J} \zeta^{\tau-1} = (p'_0 + q_0/\tau)\,\zeta^\tau + [\zeta \circ \tilde{\mathcal{J}}]\,\zeta^{\tau-1}. \]
Setting $\tau = -q_o / p'_0$ makes the first term vanish, leaving
\[ \mathcal{J} \zeta^{\tau-1} = [\zeta \circ \tilde{\mathcal{J}}]\,\zeta^{\tau-1}. \]
The equation $\mathcal{J}f = 0$ then becomes
\begin{align*}
\mathcal{J}\zeta^{\tau-1} + \mathcal{J}(\zeta^{\tau-1}\zeta\tilde{f}) & = 0 \\
\tilde{\mathcal{J}}\zeta^{\tau-1} + [\mathcal{J} \circ \zeta](\zeta^{\tau-1}\tilde{f}) & = 0 \\
\end{align*}
